---
title: "Cleaning Airbnb Data"
author: "Sarah Gaeta, Eric Gao, Gili Drior"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, message = FALSE, warning=FALSE}
setwd("~/STA160MT")
library(tidyverse)
library(readxl)
library(stringr)
library(tm)
```

```{r}
airbnb = read_csv("Airbnb_NYC_2019.csv", col_types = cols())
```


# GOAL: Clean Data

## How many entries are NA in each column?
```{r}
NA_count = data.frame(colSums(is.na(airbnb)))
colnames(NA_count) = c("NA Count")

NA_count
```

We can remove the rows with NA entries in either name or host_name.
```{r}
airbnb = airbnb[-which(is.na(airbnb$name) == T | is.na(airbnb$host_name == T)),]
```


NA entries in reviews_per_month indicate that a host has not been reviewed. Therefore, we can replace NA entries with 0. 
```{r}
airbnb$reviews_per_month[which(is.na(airbnb$reviews_per_month))] = 0
```

I am ignoring the last_review column for now... 

## Checking entries in neighbourhood and neighbourhood_group
```{r}
table(airbnb$neighbourhood_group)
table(airbnb$neighbourhood)
```

## Checking for any non-digit characters in id and host_id column
```{r}
# Goals:
# grepl both ID columns
dim(airbnb)[1] == sum(grepl("^[0-9]+$", airbnb$id))
dim(airbnb)[1] == sum(grepl("^[0-9]+$", airbnb$host_id))
```

# Clean the names column and save metadata
```{r}
# Save the number of characters
airbnb$characters_in_name = unlist(lapply(airbnb$name, nchar))

# Save the number of symbols 
#   symbols = not a character, number, or space
#   may include periods, emojis, etc
airbnb$symbols_in_name = str_count(airbnb$name, "[^A-Za-z0-9[:space:]']")

# May not be useful, but save the # of exclamation points
airbnb$exclamation_pts_in_name = str_count(airbnb$name, "!")

# Remove certain characters in a specific way
airbnb$name = gsub("[',&]", "", airbnb$name) # don't want to separate words or numbers by apostrophe, comma or &
airbnb$name = gsub("[+]", " ", airbnb$name) # some titles use + as a space 

# Finally, remove all the symbols
airbnb$name = gsub("[^A-Za-z0-9[:space:]]", "", airbnb$name)

# Save the number of numbers and capital letters
airbnb$numbers_in_name = str_count(airbnb$name, "[0-9]")
airbnb$caps_in_name = str_count(airbnb$name, "[A-Z]")

# Remove numbers
airbnb$name = gsub("[0-9]", "", airbnb$name)

# Save the number of words
word_list = str_split(airbnb$name, "[[:space:]]+")
airbnb$words_in_name = unlist(lapply(word_list, length))

# Lowercase
airbnb$name = tolower(airbnb$name)

# Remove stopwords
airbnb$name = removeWords(airbnb$name, stopwords('english'))

# Remove extra spaces
airbnb$name = gsub("[[:space:]]+", " ", airbnb$name)
airbnb$name = str_trim(airbnb$name)
```

# Clean the host_name column
```{r}
# Remove symbols
airbnb$host_name = gsub("[^A-Za-z0-9[:space:]]", " ", airbnb$host_name)
# Lowercase
airbnb$host_name = tolower(airbnb$host_name)
# Remove stopwords
airbnb$host_name = removeWords(airbnb$host_name, stopwords('english'))
# Remove extra spaces
airbnb$host_name = gsub("[[:space:]]+", " ", airbnb$host_name)
airbnb$host_name = str_trim(airbnb$host_name)
```

# Export clean data
```{r}
write.csv(airbnb, file = "clean_airbnb.csv", row.names = FALSE)
```
